### 2020-06-28 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
OptLet правка списка литературы

\bibitem{c6} Marler, R. T., Arora, J. S.: Survey of multi-objective optimization methods for engineering. Struct. Multidisciplinary Optimization 26, pp. 369--395 (2004)

@@

\bibitem{c8} Zavadskas, E. K., Turskis, Z., Kildien\.e, S.: State of art surveys of overviews on MCDM/MADM methods. Technological and Economic Development of Economy, 20, pp. 165--179 (2014)
\bibitem{c9} Hillermeier, C., Jahn, J.: Multiobjective optimization: survey of methods and industrial applications. Surv. Math. Ind. 11, pp. 1--42 (2005)
\bibitem{c10} Branke, J., Deb, K., Miettinen, K., Slowinski, R., editors.: Multi-Objective Optimization—Interactive and Evolutionary Approaches. Springer, Berlin. (2008)

@@

\bibitem{c12} Yang, X.-S.: Nature-inspired metaheuristic algorithms. Luniver Press, Frome. (2008) 

@@

\bibitem{c14} Eichfelder, G.: Scalarizations for adaptively solving multi-objective optimization problems. Comput. Optim. Appl. 44, pp. 249--273 (2009)
\bibitem{c15} Jones, D.R.: A taxonomy of global optimization methods based on response surfaces. J. Glob. Optim. 21, pp. 345--383 (2001)
\bibitem{c16} Voutchkov, I., Keane, A.: Multi-objective optimization using surrogates. Comput. Intell. Optim. Adapt. Learn. Optim. 7, pp. 155--175 (2010)
\bibitem{c17} Strongin, R.G.: Numerical methods in multiextremal problems: information-statistical algorithms. Nauka, Moscow. (1978, in Russian) 

@@

\bibitem{c22} Pint\'er, J.D.: Global optimization in Action (continuous and Lipschitz optimization: algorithms, implementations and applications). Kluwer Academic Publishers, Dortrecht. (1996)
\bibitem{c23} Sergeyev Y.D., Strongin R.G., Lera D.: Introduction to global optimization exploiting space-filling curves. Springer. (2013)

@@

\bibitem{c26} Lera D., Sergeyev Ya.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants, Communications in Nonlinear Science and Numerical Simulation, 23. pp. 328--342 (2015)
\bibitem{c27} Gergel, V.: A Unified Approach to Use of Coprocessors of Various Types for Solving Global Optimization Problems. 2nd International Conference on Mathematics and Computers in Sciences and in Industry. pp. 13--18 (2015). DOI: 10.1109/MCSI.2015.18

@@

\bibitem{c29} Bazaraa, M.S., Sherali, H.D., Shetty, C. M.: Nonlinear Programming: Theory and Algorithms, John Wiley and Sons. (2006)
\bibitem{c30} Gergel, V.P., Kozinov, E.A.: Accelerating multicriterial optimization by the intensive exploitation of accumulated search data. In: AIP Conference Proceedings, 1776. pp. 090003 (2016). DOI: 10.1063/1.4965367
\bibitem{c31} Gergel, V.P., Kozinov, E.A.: Efficient multicriterial optimization based on intensive reuse of search information.  J. Glob. Optim., 71(1). pp. 73--90 (2018). DOI: 10.1007/s10898-018-0624-3
\bibitem{c32} Sysoyev, A., Barkalov, K., Gergel, V.: Globalizer: A novel supercomputer software system for solving time-consuming global optimization problems. Numerical Algebra, Control and Optimization 8(1), pp. 47--62 (2018)
\bibitem{c33} Kvasov D.E., Sergeyev Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Advances in Engineering Software, 80, pp.58--66 (2015)
\bibitem{c34} Modorskii, V., Gaynutdinova, D., Gergel, V., Barkalov, K.: Optimization in design of scientfic products for purposes of cavitation problems. AIP Conference Proceedings, 1738. (2016)
\bibitem{c35} Evtushenko, Yu.G., Posypkin, M.A.: A deterministic algorithm for global multi-objective optimization. Optimization Methods \& Software, 29(5), pp. 1005--1019 (2014)
\bibitem{c36} {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Adaptation of a one-step worst-case optimal univariate algorithm of bi-objective Lipschitz optimization to multidimensional problems. Commun Nonlinear Sci Numer Simulat, 21, pp. 89--98 (2015)
\bibitem{c37} Gaviano, M., Kvasov, D.E, Lera, D., and Sergeyev, Ya.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM Transactions on Mathematical Software 29(4). pp. 469--480 (2003)

\bibitem{c38} Zarepisheh, M., Khorram, E.: On the transformation of lexicographic nonlinear multiobjective  programs to single objective programs. Math. Methods Oper. Res. 74. pp. 217--231 (2011)
\bibitem{c39} Haimes, Y.Y., Lasdon, L., Wismer, D.: On a bicriterion formulation of the problem of integrated systems identification and system optimization. IEEE Trans. Syst. Man Cybern. 1. pp. 296--297 (1971)
\bibitem{c40} Chankong, V., Haimes, Y.Y.: Multiobjective decision making: theory and methodology. North-Holland Series in System Science and Engineering. New York (NY): Elsevier. (1983)
\bibitem{c41} Ehrgott, M., Ruzika, S.: Improved $\varepsilon$-constraint method for multiobjective programming. J. Optim. Theory Appl. 138. pp. 375--396 (2008)
\bibitem{c42} Rastegar, N., Khorram, E.: Relaxation of constraints in lexicographic multiobjective programming problems. A Journal of Mathematical Programming and Operations Research, 64. pp. 2111--2129 (2015)
\bibitem{c43} Castro-Gutierrez, J., Landa-Silva, D., Pérez, J.M.: Improved Dynamic Lexicographic Ordering for Multi-Objective Optimisation. In: Schaefer R., Cotta C., Kolodziej J., Rudolph G. (eds) Parallel Problem Solving from Nature, PPSN XI. PPSN 2010. Lecture Notes in Computer Science, 6239. pp 31-40 (2010) 
\bibitem{c44} Audet, C., Savard, G., Zghal, W.: Multiobjective Optimization Through a Series of Single-Objective Formulations SIAM J. Optim.,19(1). pp. 188--210 (2008)
\bibitem{c45} Sergeyev, Y.D., Kvasov, D.E.: Deterministic Global Optimization: An Introduction to the Diagonal Approach (SpringerBriefs in Optimization). Springer. (2017)

@@

\bibitem{c47} Dam, E.R., Husslage, B., Hertog, D.: One-dimensional Nested Maximin Designs. Journal of Global Optimization, 46(2). pp. 287--306 (2010)
\bibitem{c48} Gergel, V., Kozinov, E.: Efficient multicriterial optimization based on intensive reuse of search information, J. Glob. Optim., 71(1). pp. 73--90 (2018). doi:10.1007/s10898-018-0624-3.
\bibitem{c49} Mart\'l, L., Garc\'la, J., Berlanga, A., Molina, J.M.: A stopping criterion for multi-objective optimization evolutionary algorithms, Information Sciences 367, pp. 700--718 (2016)
\bibitem{c50} Dilettoso, E., Rizzo, S.A., Salerno, N.: A weakly pareto compliant quality indicator. Mathematical and Computational Applications 22(1), 25 (2017)
\bibitem{c51} Wu, J., Azarm, S.: Metrics for quality assessment of a multiobjective design optimization solution set, Journal of Mechanical Design 123(1). pp. 18--25 (2001)
\bibitem{c52} Audet, C., Bigeon, J., Cartier, D., Digabel,  S. Le, Salomon, L.: Performance indicators in multiobjective optimization. G-2018-90, (2018)
\bibitem{c53} Huband, S., Hingston, P., Barone, L., and While, L.: A Review of Multiobjective Test Problems and a Scalable Test Problem Toolkit. IEEE Transactionson Evolutionary Computation, 10(5). pp. 477--506 (2006)
\bibitem{c54} Hansen, N., Auger, A., Finck, S., and Ros, R.: Real-Parameter Black-Box Optimization Benchmarking 2009: Experimental Setup. INRIA Research Report RR-6829, INRIA Saclay—Ile-de-France. updated February 2010 (2009)
\bibitem{c55} Cust\'odio, A.L., Aguilar, J.F. Madeira, Ismael Vaz, Lu\'ls N. Vicente: Direct Multisearch for Multiobjective Optimization. SIAM J. Optim. 21(3). pp. 1109--1140 (2011)
\bibitem{c56} Brockhoff, D., Tusar, T., Auger, A., Hansen, N.: Using Well-Understood Single-Objective Functions in Multiobjective Black-Box Optimization Test Suites. (2019) https://arxiv.org/abs/1604.00359 
\bibitem{c57} Cococcioni, M., Cudazzo, A., Pappalardo, M., Sergeyev, Y.D.: Solving the Lexicographic Multi-Objective Mixed-Integer Linear Programming Problem using branch-and-bound and grossone methodology, Communications in Nonlinear Science and Numerical Simulation, 84. pp. 105177 (2020)
\bibitem{c58} Cococcioni, M., Pappalardo, M., Sergeyev, Y.D.: Lexicographic multi-objective linear programming using grossone methodology: Theory and algorithm, Applied Mathematics and Computation, 318. pp. 298--311 (2018)
\bibitem{c59} Lai, L., Fiaschi, L., Cococcioni, M.: Solving Mixed Pareto-Lexicographic Multi-Objective Optimization Problems: The Case of Priority Chains, Swarm and Evolutionary Computation, 55. pp. 100687 (2020) DOI: 10.1016/j.swevo.2020.100687

>>>>

\bibitem{c6} Marler, R., Arora , J.: Survey of multi-objective optimization methods for engineering. Struct. Multidisc. Optim. \textbf{26}, 369--395 (2004)

@@

\bibitem{c8} Zavadskas, E.K., Turskis, Z., Kildien\.e, S.: State of art surveys of overviews on MCDM/MADM methods. Technol. Econ. Dev. Econ. \textbf{20}, 165--179 (2014)
\bibitem{c9} Hillermeier, C., Jahn, J.: Multiobjective optimization: survey of methods and industrial applications. Surv. Math. Ind. \textbf{11}, 1--42 (2005)
\bibitem{c10} Branke, J., Deb, K., Miettinen, K., Slowinski, R., editors.: Multi-Objective Optimization--Interactive and Evolutionary Approaches. Springer, Berlin. (2008)

@@

\bibitem{c12} Yang, X.-S.: Nature-inspired Metaheuristic Algorithms. Luniver Press, Frome. (2008) 

@@

\bibitem{c14} Eichfelder, G.: Scalarizations for adaptively solving multi-objective optimization problems. Comput. Optim. Appl. \textbf{44}, 249--273 (2009)
\bibitem{c15} Jones, D.R.: A taxonomy of global optimization methods based on response surfaces. J. Glob. Optim. \textbf{21}, 345--383 (2001)
\bibitem{c16} Voutchkov, I., Keane, A.: Multi-objective optimization using surrogates. Comput. Intell. Optim. Adapt. Learn. Optim. \textbf{7}, 155--175 (2010)
\bibitem{c17} Strongin, R.G.: Numerical Methods in Multiextremal Problems: Information-statistical Algorithms. Nauka, Moscow. (1978, in Russian) 

@@

\bibitem{c22} Pint\'er, J.D.: Global Optimization in Action (Continuous and Lipschitz Optimization: Algorithms, Implementations and Applications). Kluwer Academic Publishers, Dortrecht. (1996)
\bibitem{c23} Sergeyev, Y.D., Strongin, R.G., Lera, D.: Introduction to Global Optimization Exploiting Space-filling Curves. Springer. (2013)

@@

\bibitem{c26} Lera D., Sergeyev Ya.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Commun. Nonlinear Sci. \textbf{23}(1-3), 328--342 (2015)
\bibitem{c27} Gergel, V.: A unified approach to use of coprocessors of various types for solving global optimization problems. 2nd Int. Conf. on MACSI. 13--18 (2015). DOI: 10.1109/MCSI.2015.18

@@

\bibitem{c29} Bazaraa, M.S., Sherali, H.D., Shetty, C.M.: Nonlinear Programming: Theory and Algorithms. John Wiley and Sons. (2006)
\bibitem{c30} Gergel, V.P., Kozinov, E.A.: Accelerating multicriterial optimization by the intensive exploitation of accumulated search data. In: 	AIP Conf. Proc., \textbf{1776}, 090003 (2016). DOI: 10.1063/1.4965367
\bibitem{c31} Gergel, V.P., Kozinov, E.A.: Efficient multicriterial optimization based on intensive reuse of search information.  J. Glob. Optim. \textbf{71}(1), 73--90 (2018). DOI: 10.1007/s10898-018-0624-3
\bibitem{c32} Sysoyev, A., Barkalov, K., Gergel, V.: Globalizer: A novel supercomputer software system for solving time-consuming global optimization problems. Numer. Algebra, Control. Optim. \textbf{8}(1), 47--62 (2018)
\bibitem{c33} Kvasov D.E., Sergeyev Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Adv. Eng. Softw. \textbf{80}, 58--66 (2015)
\bibitem{c34} Modorskii, V., Gaynutdinova, D., Gergel, V., Barkalov, K.: Optimization in design of scientfic products for purposes of cavitation problems. AIP Conf. Proc. \textbf{1738}, 400013 (2016)
\bibitem{c35} Evtushenko, Yu.G., Posypkin, M.A.: A deterministic algorithm for global multi-objective optimization. Optim. Methods Softw., \textbf{29}(5), 1005--1019 (2014)
\bibitem{c36} {\v Z}ilinskas, A., {\v Z}ilinskas, J.: Adaptation of a one-step worst-case optimal univariate algorithm of bi-objective Lipschitz optimization to multidimensional problems. Commun. Nonlinear Sci. Numer. Simul., \textbf{21}(1-3), 89--98 (2015)
\bibitem{c37} Gaviano, M., Kvasov, D.E, Lera, D., and Sergeyev, Ya.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM Trans. Math. Softw. \textbf{29}(4), 469--480 (2003)

\bibitem{c38} Zarepisheh, M., Khorram, E.: On the transformation of lexicographic nonlinear multiobjective  programs to single objective programs. Math. Methods Oper. Res. \textbf{74}, 217--231 (2011)
\bibitem{c39} Haimes, Y.Y., Lasdon, L., Wismer, D.: On a bicriterion formulation of the problem of integrated systems identification and system optimization. IEEE Trans. Syst. Man Cybern. \textbf{1}, 296--297 (1971)
\bibitem{c40} Chankong, V., Haimes, Y.Y.: Multiobjective Decision Making: Theory and Methodology. North-Holland Series in System Science and Engineering. New York (NY): Elsevier. (1983)
\bibitem{c41} Ehrgott, M., Ruzika, S.: Improved $\varepsilon$-constraint method for multiobjective programming. J. Optim. Theory Appl. \textbf{138}, 375--396 (2008)
\bibitem{c42} Rastegar, N., Khorram, E.: Relaxation of constraints in lexicographic multiobjective programming problems. A Journal of Mathematical Programming and Operations Research, \textbf{64}, 2111--2129 (2015)
\bibitem{c43} Castro-Gutierrez, J., Landa-Silva, D., P\'erez, J.M.: Improved dynamic lexicographic ordering for multi-objective optimisation. Lect. Notes Comput. Sci., \textbf{6239}, 31--40 (2010) 
\bibitem{c44} Audet, C., Savard, G., Zghal, W.: Multiobjective optimization through a series of single-objective formulations. SIAM J. Optim. \textbf{19}(1), 188--210 (2008)
\bibitem{c45} Sergeyev, Y.D., Kvasov, D.E.: Deterministic Global Optimization: An Introduction to the Diagonal Approach (Springer Briefs in Optimization). Springer. (2017)

@@

\bibitem{c47} Dam, E.R., Husslage, B., Hertog, D.: One-dimensional nested maximin designs. J. Glob. Optim. \textbf{46}(2), 287--306 (2010)
\bibitem{c48} Gergel, V., Kozinov, E.: Efficient multicriterial optimization based on intensive reuse of search information, J. Glob. Optim., \textbf{71}(1), 73--90 (2018). doi:10.1007/s10898-018-0624-3.
\bibitem{c49} Mart\'l, L., Garc\'la, J., Berlanga, A., Molina, J.M.: A stopping criterion for multi-objective optimization evolutionary algorithms. Inf. Sci. \textbf{367--368}, 700--718 (2016)
\bibitem{c50} Dilettoso, E., Rizzo, S.A., Salerno, N.: A weakly pareto compliant quality indicator. Math. Comput. Appl. \textbf{22}(1), 25 (2017)
\bibitem{c51} Wu, J., Azarm, S.: Metrics for quality assessment of a multiobjective design optimization solution set. J. Mech. Des. \textbf{123}(1), 18--25 (2001)
\bibitem{c52} Audet, C., Bigeon, J., Cartier, D., Digabel, S.Le, Salomon, L.: Performance indicators in multiobjective optimization. G-2018-90, (2018)
\bibitem{c53} Huband, S., Hingston, P., Barone, L., While, L.: A review of multiobjective test problems and a scalable test problem toolkit. IEEE T. Evolut. Comput. \textbf{10}(5), 477--506 (2006)
\bibitem{c54} Hansen, N., Auger, A., Finck, S., and Ros, R.: Real-Parameter Black-Box Optimization Benchmarking 2009: Experimental Setup. INRIA Research Report RR-6829, INRIA Saclay-Ile-de-France. updated February 2010 (2009)
\bibitem{c55} Cust\'odio, A.L., Madeira, J.F.A., Vaz, A.I.F., Vicente, L.N.: Direct multisearch for multiobjective optimization. SIAM J. Optim. \textbf{21}(3), 1109--1140 (2011)
\bibitem{c56} Brockhoff, D., Tusar, T., Auger, A., Hansen, N.: Using well-understood single-objective functions in multiobjective black-box optimization test suites. (2019) https://arxiv.org/abs/1604.00359 
\bibitem{c57} Cococcioni, M., Cudazzo, A., Pappalardo, M., Sergeyev, Y.D.: Solving the lexicographic multi-objective mixed-integer linear programming problem using branch-and-bound and grossone methodology. Commun. Nonlinear Sci. Numer. Simul. \textbf{84}, 105177 (2020)
\bibitem{c58} Cococcioni, M., Pappalardo, M., Sergeyev, Y.D.: Lexicographic multi-objective linear programming using grossone methodology: Theory and algorithm. Appl. Math. Comput. \textbf{318}, 298--311 (2018)
\bibitem{c59} Lai, L., Fiaschi, L., Cococcioni, M.: Solving mixed pareto-lexicographic multi-objective optimization problems: the case of priority chains. Swarm Evol. Comput. \textbf{55}, 100687 (2020) DOI: 10.1016/j.swevo.2020.100687
